---
title: "cmetcalf_OriginalHomeworkCode_02"
author: "Cat Metcalf"
date: "2023-09-25"
output: 
 prettydoc::html_pretty:
   toc: true
   theme: cayman
   
---

# Titis in the Mist

Every Saturday morning, at the same time, a primatologist goes and sits in the forest to listen for titi monkey calls, counting the number of calls they hear in a 2 hour window from 5am to 7am. Based on previous knowledge, she believes that the mean number of calls she will hear in that time is exactly 15. Let X represent the appropriate Poisson random variable of the number of calls heard in each monitoring session.

## What is the probability that she will hear more than 8 calls during any given session?

```{r}
ppois(8, lambda=15, lower.tail = FALSE) #calculates probability of getting value greater than 8 within time interval
```


## What is the probability that she will hear no calls in a session?

```{r}
x <-ppois(0, lambda=15) #0 indicates there are no calls in the time interval
x^2 #squared because probabilities must be within 0 and 1
```

## What is the probability that she will hear exactly 3 calls in a session?

```{r}
ppois(3, lambda = 15, log.p = FALSE)
```
Does this actually give the output that only 3 events occurred over time interval?
## Plot the relevant Poisson mass function over the values in range 0 ≤ x ≤ 30.

```{r}
x <- 0:30
l = 15
probset <- dpois(x = x, lambda = l)
barplot(probset, names.arg = x, space = 0, xlab = "x", ylab = "Pr(X = x)", main = "Probability Mass Function")
```

## Simulate 104 results from this distribution (i.e., 2 years of Saturday monitoring sessions).

```{r}
m <- rpois(104, lambda = 15)
m
```

## Plot the simulated results using hist() and use xlim() to set the horizontal limits to be from 0 to 30. How does your histogram compare to the shape of the probability mass function you plotted above?

```{r}
hist(m, probability = TRUE) +
  xlim(0,30)
```
Gave "Error in xlim(0, 30) : could not find function "xlim"" but still set 0, 30 x limits?

Distribution shifts left with higher values occurring earlier in the range of x compared to the probability mass function above.


